---
title: "NFL 2025 Season Analysis"
subtitle: "League Overview · Offense & Defense Tendencies · QB Profiles · Skill Positions"
date: "`r format(Sys.Date(), '%B %Y')`"
output:
  html_document:
    theme: "bootstrap"
    highlight: null
    self_contained: true
    css: [styles_dark_vars.css, styles_base.css]
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo    = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.width  = 12,
  fig.height = 7,
  dpi = 150
)

theme_set(theme_sharp(colors = palette_light))

bg      <- palette_light$bg
panel   <- palette_light$panel
grid    <- palette_light$grid
text_c  <- palette_light$text
muted   <- palette_light$muted
accent  <- palette_light$accent
accent2 <- palette_light$accent2
green_c <- palette_light$green
red_c   <- palette_light$red
```

# Team Pages {.section-header}

Click a team to view their full team report — pass rate tendencies, draft class, trades, and free agent signings, styled in that team's own colors.

```{r team-index, results='asis'}
cat('<div class="team-grid">\n')
for (tm in all_teams) {
  tm_row <- teams |> filter(team_abbr == tm)
  logo <- tm_row$team_logo_espn[1]
  name <- tm_row$team_name[1]
  cat(glue(
    '<a class="team-tile" href="teams/{tm}.html" title="{name}">',
    '<img src="{logo}" alt="{tm}"><span>{tm}</span></a>\n'
  ))
}
cat('</div>\n')
```

---

# Offense Tendencies {.section-header}

```{r offense-epa}
# ── EPA/play & Success Rate ────────────────────────────────────────────────────
avg_epa <- mean(epa_off$epa_per_play)
avg_sr  <- mean(epa_off$success_rate)

ggplot(epa_off, aes(x = success_rate, y = epa_per_play)) +
  geom_hline(yintercept = avg_epa, color = muted, linetype = "dashed", linewidth = 0.4) +
  geom_vline(xintercept = avg_sr,  color = muted, linetype = "dashed", linewidth = 0.4) +
  geom_point(aes(color = team_color), size = 4, alpha = 0.9) +
  scale_color_identity() +
  geom_label_repel(
    aes(label = team, fill = team_color, color = team_color2),
    size = 2.5, fontface = "bold",
    box.padding = 0.4, max.overlaps = 32,
    label.size = 0
  ) +
  scale_fill_identity() +
  annotate("text", x = max(epa_off$success_rate) * 0.99, y = max(epa_off$epa_per_play) * 0.97,
           label = "ELITE OFFENSE", color = green_c, size = 2.8, hjust = 1, fontface = "bold") +
  annotate("text", x = min(epa_off$success_rate) * 1.01, y = min(epa_off$epa_per_play) * 0.97,
           label = "REBUILD MODE", color = red_c, size = 2.8, hjust = 0, fontface = "bold") +
  labs(
    title    = "Offensive EPA/Play vs. Success Rate — 2025",
    subtitle = "Regular season only · Dashed lines = league average",
    x = "Success Rate", y = "EPA / Play",
    caption  = "Data: nflfastR / nflverse"
  ) +
  scale_x_continuous(labels = percent_format(accuracy = 1)) +
  theme(legend.position = "none")
```

```{r offense-edpr}
# ── Early Down Pass Rate ────────────────────────────────────────────────────────
ggplot(edpr, aes(x = reorder(team, EDPR), y = EDPR)) +
  geom_col(aes(fill = ifelse(EDPR > mean(EDPR), accent, muted)), width = 0.75) +
  geom_hline(yintercept = mean(edpr$EDPR), color = accent2, linetype = "dashed", linewidth = 0.5) +
  scale_fill_identity() +
  coord_flip() +
  scale_y_continuous(labels = percent_format(accuracy = 1), expand = expansion(mult = c(0, 0.05))) +
  labs(
    title    = "Early Down Pass Rate (EDPR) — 2025",
    subtitle = "Downs 1 & 2 · Orange dashed = league average · Warren Sharp signature metric",
    x = NULL, y = "Pass Rate on 1st & 2nd Down",
    caption  = "Data: nflfastR / nflverse"
  )
```

```{r offense-down-distance}
# ── Run/Pass Rate by Down & Distance ──────────────────────────────────────────
rd_splits <- reg |>
  filter(down %in% c(1, 2, 3)) |>
  mutate(
    ydstogo_bucket = case_when(
      ydstogo <= 2  ~ "Short\n(1-2 yds)",
      ydstogo <= 5  ~ "Medium\n(3-5 yds)",
      ydstogo <= 9  ~ "Standard\n(6-9 yds)",
      ydstogo <= 14 ~ "Long\n(10-14 yds)",
      TRUE          ~ "Very Long\n(15+)"
    ),
    ydstogo_bucket = factor(ydstogo_bucket, levels = c(
      "Short\n(1-2 yds)", "Medium\n(3-5 yds)", "Standard\n(6-9 yds)",
      "Long\n(10-14 yds)", "Very Long\n(15+)"
    )),
    down_label = paste0(down, ifelse(down == 1, "st", ifelse(down == 2, "nd", "rd")), " Down")
  ) |>
  group_by(down_label, ydstogo_bucket) |>
  summarise(
    pass_rate = mean(pass == 1),
    epa       = mean(epa),
    n         = n(),
    .groups   = "drop"
  )

ggplot(rd_splits, aes(x = ydstogo_bucket, y = pass_rate, fill = epa)) +
  geom_col(width = 0.8) +
  geom_text(aes(label = percent(pass_rate, accuracy = 1)),
            vjust = -0.4, color = text_c, size = 2.8, fontface = "bold") +
  facet_wrap(~down_label) +
  scale_fill_gradient2(
    low = red_c, mid = muted, high = green_c, midpoint = 0,
    name = "EPA/Play"
  ) +
  scale_y_continuous(labels = percent_format(accuracy = 1), expand = expansion(mult = c(0, 0.12))) +
  labs(
    title    = "League-Wide Pass Rate by Down & Distance — 2025",
    subtitle = "Color = EPA/play on pass plays · Regular season",
    x = "Yards to Go", y = "Pass Rate",
    caption  = "Data: nflfastR / nflverse"
  )
```

```{r offense-playaction, eval=!is.null(ftn)}
# ── Play-Action Usage & EPA ────────────────────────────────────────────────────
if (!is.null(ftn) && "is_play_action" %in% names(ftn)) {
  pa_data <- ftn |>
    filter(!is.na(is_play_action)) |>
    left_join(
      reg |> select(game_id, play_id, epa, posteam),
      by = c("nflverse_game_id" = "game_id", "nflverse_play_id" = "play_id")
    ) |>
    filter(!is.na(epa), !is.na(posteam)) |>
    group_by(posteam) |>
    summarise(
      pa_rate     = mean(is_play_action, na.rm = TRUE),
      pa_epa      = mean(epa[is_play_action == TRUE], na.rm = TRUE),
      no_pa_epa   = mean(epa[is_play_action == FALSE], na.rm = TRUE),
      pa_lift     = pa_epa - no_pa_epa,
      n           = n(),
      .groups     = "drop"
    ) |>
    rename(team = posteam) |>
    add_team_colors() |>
    arrange(desc(pa_rate))

  ggplot(pa_data, aes(x = pa_rate, y = pa_lift)) +
    geom_hline(yintercept = 0, color = muted, linewidth = 0.4) +
    geom_vline(xintercept = mean(pa_data$pa_rate), color = muted, linetype = "dashed", linewidth = 0.4) +
    geom_point(aes(color = team_color), size = 4) +
    scale_color_identity() +
    geom_label_repel(
      aes(label = team, fill = team_color, color = team_color2),
      size = 2.5, fontface = "bold", box.padding = 0.4,
      label.size = 0, max.overlaps = 32
    ) +
    scale_fill_identity() +
    scale_x_continuous(labels = percent_format(accuracy = 1)) +
    labs(
      title    = "Play-Action: Usage Rate vs. EPA Lift — 2025",
      subtitle = "EPA lift = PA EPA minus non-PA EPA · Dashed = avg usage rate",
      x = "Play-Action Rate", y = "EPA Lift from Play-Action",
      caption  = "Data: FTN Charting / nflverse"
    ) +
    theme(legend.position = "none")
}
```

```{r offense-table}
# ── Offense Summary Table ─────────────────────────────────────────────────────
off_table <- reg |>
  group_by(posteam) |>
  summarise(
    epa_play    = mean(epa),
    success_rt  = mean(success, na.rm = TRUE),
    pass_rate   = mean(pass == 1),
    avg_air_yds = mean(air_yards, na.rm = TRUE),
    yac_avg     = mean(yards_after_catch, na.rm = TRUE),
    n_plays     = n(),
    .groups     = "drop"
  ) |>
  left_join(
    reg |> filter(down %in% c(1,2)) |>
      group_by(posteam) |>
      summarise(edpr = mean(pass == 1), .groups = "drop"),
    by = "posteam"
  ) |>
  rename(team = posteam) |>
  left_join(teams |> select(team_abbr, team_logo_espn, team_color),
            by = c("team" = "team_abbr")) |>
  arrange(desc(epa_play))

off_table |>
  select(team_logo_espn, team, epa_play, success_rt, edpr, pass_rate, avg_air_yds, yac_avg) |>
  gt() |>
  gt_img_rows(columns = team_logo_espn, height = 25) |>
  fmt_number(columns = c(epa_play, avg_air_yds, yac_avg), decimals = 2) |>
  fmt_percent(columns = c(success_rt, edpr, pass_rate), decimals = 1) |>
  cols_label(
    team_logo_espn = "",
    team       = "Team",
    epa_play   = "EPA/Play",
    success_rt = "Success%",
    edpr       = "EDPR",
    pass_rate  = "Pass%",
    avg_air_yds = "Air Yds",
    yac_avg    = "YAC"
  ) |>
  gt_color_rows(epa_play,   palette = c(red_c, panel, green_c), domain = c(-0.25, 0.25)) |>
  gt_color_rows(success_rt, palette = c(red_c, panel, green_c), domain = c(0.35, 0.55)) |>
  gt_color_rows(edpr,       palette = c(red_c, panel, green_c), domain = c(0.45, 0.70)) |>
  tab_header(title = "2025 Offensive Tendencies — All Teams") |>
  tab_options(
    table.background.color        = panel,
    column_labels.background.color = grid,
    row.striping.background_color  = bg,
    table.font.color               = text_c,
    table.font.size                = px(12),
    heading.background.color       = bg,
    heading.title.font.size        = px(14)
  )
```

---

# Defense Tendencies {.section-header}

```{r defense-epa}
# ── Defensive EPA Allowed ──────────────────────────────────────────────────────
avg_epa_d <- mean(epa_def$epa_allowed)
avg_sr_d  <- mean(epa_def$success_allowed)

ggplot(epa_def, aes(x = success_allowed, y = epa_allowed)) +
  geom_hline(yintercept = avg_epa_d, color = muted, linetype = "dashed", linewidth = 0.4) +
  geom_vline(xintercept = avg_sr_d,  color = muted, linetype = "dashed", linewidth = 0.4) +
  geom_point(aes(color = team_color), size = 4, alpha = 0.9) +
  scale_color_identity() +
  geom_label_repel(
    aes(label = team, fill = team_color, color = team_color2),
    size = 2.5, fontface = "bold",
    box.padding = 0.4, max.overlaps = 32, label.size = 0
  ) +
  scale_fill_identity() +
  annotate("text", x = min(epa_def$success_allowed) * 1.01,
           y = min(epa_def$epa_allowed) * 0.97,
           label = "ELITE DEFENSE", color = green_c, size = 2.8, hjust = 0, fontface = "bold") +
  annotate("text", x = max(epa_def$success_allowed) * 0.99,
           y = max(epa_def$epa_allowed) * 0.97,
           label = "SIEVE DEFENSE", color = red_c, size = 2.8, hjust = 1, fontface = "bold") +
  labs(
    title    = "Defensive EPA Allowed vs. Success Rate Allowed — 2025",
    subtitle = "Lower = better · Dashed lines = league average · Regular season",
    x = "Success Rate Allowed", y = "EPA / Play Allowed",
    caption  = "Data: nflfastR / nflverse"
  ) +
  scale_x_continuous(labels = percent_format(accuracy = 1)) +
  theme(legend.position = "none")
```

```{r defense-pass-run}
# ── Pass vs Run Defense Split ──────────────────────────────────────────────────
def_split <- epa_def |>
  select(team, team_color, pass_epa_all, run_epa_all) |>
  pivot_longer(cols = c(pass_epa_all, run_epa_all),
               names_to = "type", values_to = "epa") |>
  mutate(type = ifelse(type == "pass_epa_all", "Pass Defense", "Run Defense"))

ggplot(def_split |> arrange(type, epa),
       aes(x = reorder(team, epa), y = epa, fill = type)) +
  geom_col(position = "dodge", width = 0.7) +
  geom_hline(yintercept = 0, color = text_c, linewidth = 0.3) +
  scale_fill_manual(values = c("Pass Defense" = accent, "Run Defense" = accent2)) +
  coord_flip() +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.05))) +
  labs(
    title    = "EPA Allowed: Pass vs. Run Defense — 2025",
    subtitle = "Lower EPA allowed = better defense · Regular season",
    x = NULL, y = "EPA / Play Allowed", fill = NULL,
    caption  = "Data: nflfastR / nflverse"
  ) +
  theme(legend.position = "top")
```

```{r defense-third-down}
# ── 3rd Down Defense ──────────────────────────────────────────────────────────
ggplot(third_def, aes(x = reorder(team, conv_allowed), y = conv_allowed)) +
  geom_col(aes(fill = ifelse(conv_allowed < mean(conv_allowed), green_c, red_c)), width = 0.75) +
  geom_hline(yintercept = mean(third_def$conv_allowed),
             color = accent2, linetype = "dashed", linewidth = 0.5) +
  scale_fill_identity() +
  coord_flip() +
  scale_y_continuous(labels = percent_format(accuracy = 1),
                     expand = expansion(mult = c(0, 0.05))) +
  labs(
    title    = "3rd Down Conversion Rate Allowed — 2025",
    subtitle = "Green = better than average · Orange dashed = league average",
    x = NULL, y = "3rd Down Conversion Rate Allowed",
    caption  = "Data: nflfastR / nflverse"
  )
```

```{r defense-table}
# ── Defense Summary Table ──────────────────────────────────────────────────────
def_table <- reg |>
  group_by(defteam) |>
  summarise(
    epa_allowed  = mean(epa),
    success_all  = mean(success, na.rm = TRUE),
    pass_epa_all = mean(epa[pass == 1], na.rm = TRUE),
    run_epa_all  = mean(epa[rush == 1], na.rm = TRUE),
    .groups      = "drop"
  ) |>
  left_join(
    reg |> filter(down == 3) |>
      group_by(defteam) |>
      summarise(third_conv_all = mean(first_down == 1, na.rm = TRUE), .groups = "drop"),
    by = "defteam"
  ) |>
  rename(team = defteam) |>
  left_join(teams |> select(team_abbr, team_logo_espn),
            by = c("team" = "team_abbr")) |>
  arrange(epa_allowed)

def_table |>
  select(team_logo_espn, team, epa_allowed, success_all, pass_epa_all, run_epa_all, third_conv_all) |>
  gt() |>
  gt_img_rows(columns = team_logo_espn, height = 25) |>
  fmt_number(columns = c(epa_allowed, pass_epa_all, run_epa_all), decimals = 2) |>
  fmt_percent(columns = c(success_all, third_conv_all), decimals = 1) |>
  cols_label(
    team_logo_espn = "",
    team          = "Team",
    epa_allowed   = "EPA Allowed",
    success_all   = "Success% All",
    pass_epa_all  = "Pass EPA All",
    run_epa_all   = "Run EPA All",
    third_conv_all = "3rd Conv All"
  ) |>
  gt_color_rows(epa_allowed,   palette = c(green_c, panel, red_c), domain = c(-0.25, 0.25)) |>
  gt_color_rows(success_all,   palette = c(green_c, panel, red_c), domain = c(0.35, 0.55)) |>
  gt_color_rows(third_conv_all,palette = c(green_c, panel, red_c), domain = c(0.30, 0.50)) |>
  tab_header(title = "2025 Defensive Tendencies — All Teams") |>
  tab_options(
    table.background.color         = panel,
    column_labels.background.color = grid,
    row.striping.background_color  = bg,
    table.font.color               = text_c,
    table.font.size                = px(12),
    heading.background.color       = bg,
    heading.title.font.size        = px(14)
  )
```

---

# QB Profiles {.section-header}

```{r qb-cpoe-epa}
# ── CPOE vs EPA/Attempt ────────────────────────────────────────────────────────
avg_cpoe <- mean(qb_base$cpoe)
avg_epa_att <- mean(qb_base$epa_att)

ggplot(qb_base, aes(x = cpoe, y = epa_att)) +
  geom_hline(yintercept = avg_epa_att, color = muted, linetype = "dashed", linewidth = 0.4) +
  geom_vline(xintercept = avg_cpoe,    color = muted, linetype = "dashed", linewidth = 0.4) +
  geom_point(aes(color = team_color), size = 5, alpha = 0.9) +
  scale_color_identity() +
  geom_label_repel(
    aes(label = passer, fill = team_color, color = team_color2),
    size = 2.4, fontface = "bold", box.padding = 0.5,
    label.size = 0, max.overlaps = 32
  ) +
  scale_fill_identity() +
  labs(
    title    = "QB CPOE vs. EPA/Attempt — 2025",
    subtitle = "Min 150 attempts · CPOE = completion % over expected · Dashed = averages",
    x = "CPOE (%)", y = "EPA / Attempt",
    caption  = "Data: nflfastR / nflverse"
  ) +
  annotate("text", x = max(qb_base$cpoe) * 0.97, y = max(qb_base$epa_att) * 0.96,
           label = "ELITE", color = green_c, size = 3, fontface = "bold", hjust = 1) +
  theme(legend.position = "none")
```

```{r qb-air-yards}
# ── Air Yards (Aggressiveness) ─────────────────────────────────────────────────
ggplot(qb_base |> arrange(desc(air_yds)),
       aes(x = reorder(passer, air_yds), y = air_yds)) +
  geom_col(aes(fill = ifelse(air_yds > mean(air_yds), accent, muted)), width = 0.75) +
  geom_hline(yintercept = mean(qb_base$air_yds), color = accent2,
             linetype = "dashed", linewidth = 0.5) +
  scale_fill_identity() +
  coord_flip() +
  labs(
    title    = "Average Air Yards per Attempt — 2025",
    subtitle = "Proxy for QB aggressiveness / depth of target · Min 150 attempts",
    x = NULL, y = "Avg Air Yards",
    caption  = "Data: nflfastR / nflverse"
  )
```

```{r qb-ngs, eval=!is.null(ngs_pass)}
# ── NGS: Time to Throw + Aggressiveness ───────────────────────────────────────
if (!is.null(ngs_pass) && nrow(ngs_pass) > 0) {
  ngs_season <- ngs_pass |>
    filter(!is.na(avg_time_to_throw), !is.na(aggressiveness)) |>
    group_by(player_display_name, player_gsis_id, team_abbr) |>
    summarise(
      avg_ttt     = mean(avg_time_to_throw, na.rm = TRUE),
      aggression  = mean(aggressiveness, na.rm = TRUE),
      avg_air_yds = mean(avg_intended_air_yards, na.rm = TRUE),
      .groups     = "drop"
    ) |>
    semi_join(qb_base, by = c("player_gsis_id" = "passer_id")) |>
    rename(team = team_abbr) |>
    add_team_colors()

  if (nrow(ngs_season) >= 5) {
    ggplot(ngs_season, aes(x = avg_ttt, y = aggression)) +
      geom_point(aes(color = team_color), size = 5) +
      scale_color_identity() +
      geom_label_repel(
        aes(label = player_display_name, fill = team_color, color = team_color2),
        size = 2.4, fontface = "bold", box.padding = 0.4, label.size = 0
      ) +
      scale_fill_identity() +
      labs(
        title    = "NGS: Time to Throw vs. Aggressiveness% — 2025",
        subtitle = "Aggressiveness = % of passes into tight coverage · Source: Next Gen Stats",
        x = "Avg Time to Throw (sec)", y = "Aggressiveness %",
        caption  = "Data: NFL Next Gen Stats via nflverse"
      ) +
      scale_y_continuous(labels = percent_format(accuracy = 1, scale = 1)) +
      theme(legend.position = "none")
  }
}
```

```{r qb-table}
# ── QB Summary Table ───────────────────────────────────────────────────────────
qb_table_data <- qb_base |>
  arrange(desc(epa_att))

qb_table_data |>
  select(team_logo_espn, passer, team, attempts, cpoe, epa_att, air_yds) |>
  gt() |>
  gt_img_rows(columns = team_logo_espn, height = 25) |>
  fmt_number(columns = c(cpoe, epa_att, air_yds), decimals = 2) |>
  fmt_number(columns = attempts, decimals = 0) |>
  cols_label(
    team_logo_espn = "",
    passer    = "QB",
    team      = "Team",
    attempts  = "Att",
    cpoe      = "CPOE",
    epa_att   = "EPA/Att",
    air_yds   = "Air Yds"
  ) |>
  gt_color_rows(cpoe,    palette = c(red_c, panel, green_c), domain = c(-10, 10)) |>
  gt_color_rows(epa_att, palette = c(red_c, panel, green_c), domain = c(-0.3, 0.4)) |>
  tab_header(title = "2025 QB Profiles — Qualified Passers (150+ Att)") |>
  tab_options(
    table.background.color         = panel,
    column_labels.background.color = grid,
    row.striping.background_color  = bg,
    table.font.color               = text_c,
    table.font.size                = px(12),
    heading.background.color       = bg,
    heading.title.font.size        = px(14)
  )
```

---

# Skill Positions {.section-header}

```{r receivers-targets}
# ── Receiver Target Share & YAC ────────────────────────────────────────────────
ggplot(rec_base |> slice_max(targets, n = 40),
       aes(x = air_yds, y = yac)) +
  geom_point(aes(color = team_color, size = target_share), alpha = 0.85) +
  scale_color_identity() +
  scale_size_continuous(range = c(2, 8), labels = percent_format(accuracy = 1),
                        name = "Target Share") +
  geom_label_repel(
    aes(label = receiver, fill = team_color, color = team_color2),
    size = 2.2, fontface = "bold", box.padding = 0.3,
    label.size = 0, max.overlaps = 25
  ) +
  scale_fill_identity() +
  labs(
    title    = "Air Yards vs. YAC — Top Receivers 2025",
    subtitle = "Bubble size = target share · Top 40 by targets · Min 50 targets",
    x = "Avg Air Yards (Depth of Target)", y = "Avg YAC",
    caption  = "Data: nflfastR / nflverse"
  )
```

```{r receivers-epa}
# ── Top Receivers by EPA/Target ────────────────────────────────────────────────
top_rec <- rec_base |>
  slice_max(epa_target, n = 25)

ggplot(top_rec, aes(x = reorder(receiver, epa_target), y = epa_target)) +
  geom_col(aes(fill = team_color), width = 0.75) +
  scale_fill_identity() +
  geom_text(aes(label = round(epa_target, 2)),
            hjust = -0.15, color = text_c, size = 2.8) +
  coord_flip() +
  scale_y_continuous(expand = expansion(mult = c(0, 0.15))) +
  labs(
    title    = "Top 25 Receivers by EPA/Target — 2025",
    subtitle = "Min 50 targets · Regular season",
    x = NULL, y = "EPA / Target",
    caption  = "Data: nflfastR / nflverse"
  )
```

```{r rushers}
# ── Top Rushers by EPA/Carry ───────────────────────────────────────────────────
ggplot(rush_base, aes(x = ypc, y = epa_carry)) +
  geom_hline(yintercept = 0, color = muted, linewidth = 0.3) +
  geom_vline(xintercept = mean(rush_base$ypc), color = muted,
             linetype = "dashed", linewidth = 0.4) +
  geom_point(aes(color = team_color, size = carries), alpha = 0.85) +
  scale_color_identity() +
  scale_size_continuous(range = c(2, 8), name = "Carries") +
  geom_label_repel(
    aes(label = rusher, fill = team_color, color = team_color2),
    size = 2.2, fontface = "bold", box.padding = 0.4,
    label.size = 0, max.overlaps = 30
  ) +
  scale_fill_identity() +
  labs(
    title    = "Rushing: YPC vs. EPA/Carry — 2025",
    subtitle = "Min 60 carries · Bubble size = carry volume",
    x = "Yards Per Carry", y = "EPA / Carry",
    caption  = "Data: nflfastR / nflverse"
  )
```

```{r ngs-receivers, eval=!is.null(ngs_rec)}
# ── NGS Receiving: Separation & Cushion ───────────────────────────────────────
if (!is.null(ngs_rec) && nrow(ngs_rec) > 0 &&
    "avg_separation" %in% names(ngs_rec)) {
  ngs_rec_season <- ngs_rec |>
    filter(!is.na(avg_separation)) |>
    group_by(player_display_name, player_gsis_id, team_abbr) |>
    summarise(
      sep         = mean(avg_separation, na.rm = TRUE),
      cushion     = mean(avg_cushion, na.rm = TRUE),
      catch_pct   = mean(catch_percentage, na.rm = TRUE),
      .groups     = "drop"
    ) |>
    semi_join(rec_base, by = c("player_gsis_id" = "receiver_id")) |>
    rename(team = team_abbr) |>
    add_team_colors()

  if (nrow(ngs_rec_season) >= 5) {
    ggplot(ngs_rec_season, aes(x = cushion, y = sep)) +
      geom_point(aes(color = team_color), size = 4, alpha = 0.85) +
      scale_color_identity() +
      geom_label_repel(
        aes(label = player_display_name, fill = team_color, color = team_color2),
        size = 2.2, fontface = "bold", box.padding = 0.4, label.size = 0
      ) +
      scale_fill_identity() +
      labs(
        title    = "NGS: Pre-Snap Cushion vs. Separation at Catch — 2025",
        subtitle = "Source: NFL Next Gen Stats · Qualified receivers (50+ targets)",
        x = "Avg Pre-Snap Cushion (yds)", y = "Avg Separation at Catch (yds)",
        caption  = "Data: NFL Next Gen Stats via nflverse"
      ) +
      theme(legend.position = "none")
  }
}
```

---

*Report generated `r format(Sys.time(), '%Y-%m-%d %H:%M')` · Data: nflfastR / nflreadr / nflverse · NGS: NFL Next Gen Stats*
